\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-07-28 syntax.tex
resolve comment

Then any field using "Wsup" and "Wrec", directly relying on the
$\bW\sigma$ in the context (can be spotted from \ruleref{Ind-Term} and
\ruleref{Rec-Constr}), and responsible for exhaustiveness checking will be non-inheritable---in these cases, "Wsup"
can be understood as concrete constructors and "Wrec" are
\textit{exhaustiveness checking}. These fields together with inductive
types are the ones sealing is responsible for hiding.\YZ{Is sealing really hiding these fields (that use Wsup and Wrec), or is it that the concrete definition of an inductive type is not hidden for these fields so that they can assume knowledge about the inductive type's signature?}\EDJreply{More rigourously speaking, sealing is only hiding the $\tau$ appearing in $\bW \tau$, it never tries to hide (or make absence of) any field. But for the people that are only looking at the interface/type, the people cannot if a field is a constructor (using Wsup) or a normal function. \\
The concrete definition of an inductive type (i.e.  $\bW \tau$) is definitely hidden and those inductive type will thus have type $\cU$. After the $\tau$ is hidden, the programmer is assuming knowledge of the inductive type.
}\YZreply{The sentence feels confusing because "these fields" are not sealed; rather, as you explain below, there's no need to seal anything when, say, doing exhaustiveness checking using Wrec.}
After compilation
of linkage types into existential types, we can easily hide the
\textit{concrete} definition of the inductive type while exposing all
the fields that use "Wsup" and "Wrec" as an abstract interface.
Apparently, future fields relying on this abstract interface will have no
problem on inheritance. 
For example, $t_{new}$ above cannot be doing \textit{exhaustiveness
checking}, but it can freely use any \textit{exhaustiveness-checked}
recursor, and also inheritable.
Of course, since "Wsup" and "Wrec" directly rely on the concrete inductive definition, we will have to override these fields whenever inductive type is overridden. For "Wsup" we only need to override each constructor and for "Wrec" it is just doing exhaustiveness checking inside each children family. The recursor handlers however, like plugin implementation, can be safely inherited.
\YZ{I suppose the terminology 'sealing' is a reference to ML modules? In
ML, sealing has the connotation of hiding things behind an existential
type. So using the same word may cause the reader to have false
presumptions about what is going on here.}\EDJreply{You are right. Our "Sealing" is not hiding a particular field into an existential type, but our seal is make several fields together into an "existential type". Basically it hides the concrete definition of inductive type so that future fields doesn't have to be defined upon that.}\EDJreply{I will resolve this comment once I add the throughout example and you find it clear---because I haven't changed any text}

>>>>

Then any field using "Wsup" and "Wrec", directly relying on the
$\bW\sigma$ in the context (can be spotted from \ruleref{Ind-Term} and
\ruleref{Rec-Constr}), and responsible for exhaustiveness checking will be non-inheritable---in these cases, "Wsup"
can be understood as concrete constructors and "Wrec" are
\textit{exhaustiveness checking}. These fields together with inductive
types are the ones sealing is responsible for hiding.
%\YZ{Is sealing really hiding these fields (that use Wsup and Wrec), or is it that the concrete definition of an inductive type is not hidden for these fields so that they can assume knowledge about the inductive type's signature?}\EDJreply{More rigourously speaking, sealing is only hiding the $\tau$ appearing in $\bW \tau$, it never tries to hide (or make absence of) any field.
%}\YZreply{The sentence feels confusing because "these fields" are not sealed; rather, as you explain below, there's no need to seal anything when, say, doing exhaustiveness checking using Wrec.}\EDJreply{Oh I see. The sentence here I say "fields and the inductive type" are sealed together because the sealing function will be between big sigma (Sig T:$\bW \sigma$, c1 : El (W T) -> El (W T)) and (Sig T:$\cU$, c1 : El T -> El T). That is the reason I say ``sealed together'' here. The (constructor) fields (e.g. c1) are not literally hidden, but their type are changed *together* with the former type T, because of type-dependency. }
After compilation
of linkage types into existential types, we can easily hide the
\textit{concrete} definition of the inductive type while exposing all
the fields that use "Wsup" and "Wrec" as an abstract interface.
Apparently, future fields relying on this abstract interface will have no
problem on inheritance. 
For example, $t_{new}$ above cannot be doing \textit{exhaustiveness
checking}, but it can freely use any \textit{exhaustiveness-checked}
recursor, and also inheritable.
Of course, since "Wsup" and "Wrec" directly rely on the concrete inductive definition, we will have to override these fields whenever inductive type is overridden. For "Wsup" we only need to override each constructor and for "Wrec" it is just doing exhaustiveness checking inside each children family. The recursor handlers however, like plugin implementation, can be safely inherited.
\YZ{I suppose the terminology 'sealing' is a reference to ML modules? In
ML, sealing has the connotation of hiding things behind an existential
type. So using the same word may cause the reader to have false
presumptions about what is going on here.}\EDJreply{You are right. Our "Sealing" is not hiding a particular field into an existential type, but our seal is make several fields together into an "existential type". Basically it hides the concrete definition of inductive type so that future fields doesn't have to be defined upon that.}\EDJreply{I will resolve this comment once I add the throughout example and you find it clear---because I haven't changed any text}
